---
title: 'Peer-graded Assignment: Course Project: Shiny Application and Reproducible
  Pitch'
author: "Sherwood Tang"
date: "July 19, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Shiny Application and Reproducible

This is an application aimming at showing the simple linear regression between Ozone and variables from the built-in dataset Airquality. 

Here are variables we focus on:

- Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island
- Solar.R: Solar radiation in Langleys in the frequency band 4000-7700 Angstroms from 0800 to 1200 hours at Central Park
- Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport
- Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.


## ui Code

```{r, eval = FALSE}
library(shiny)

shinyUI(
  navbarPage("Shiny App for Airquality Dataset",
             tabPanel("Analysis and Plot",
                      fluidPage(
                        titlePanel("Simple Linear Relationship between Ozone and other variables"),
                        sidebarLayout(
                          sidebarPanel(
                            selectInput("variable", "Variable:",
                                        c("Solar R (lang)" = "Solar.R",
                                          "Wind (mph)" = "Wind",
                                          "Temperature (degrees F)" = "Temp")),
                            checkboxInput("outliers", "Show BoxPlot's outliers", FALSE)
                          ),
                          
                          mainPanel(
                          h3(textOutput("caption")),
                          
                          tabsetPanel(type = "tabs",
                                      tabPanel("BoxPlot", plotOutput("OzoneBoxPlot")),
                                      tabPanel("Simple Regression Model",
                                               plotOutput("OzonePlot"),
                                               verbatimTextOutput("fit")
                                               )
                                      )
                          )
                        )
                        )
                      ),
             tabPanel("My Github Repository",
                      a("https://github.com/tongmanhok/Peer-graded-Assignment-Course-Project-Shiny-Application-and-Reproducible-Pitch"),
                      hr(),
                      h2("Thank you!")
                      )
             )
            )

```


## server Code

```{r, eval = FALSE}
library(shiny)
library(datasets)

data <- airquality

shinyServer(function(input, output){
  
  model <- reactive({
    paste("Ozone ~ ", input$variable)
  })
  
  modeltext <- reactive({
    paste("Ozone ~ ", "as.integer(", input$variable, ")")
  })
  
  fit <- reactive({
    lm(as.formula(modeltext()), data = data)
  })
  
  output$cation <- renderText({
    model()
  })
  
  output$OzoneBoxPlot <- renderPlot({
    boxplot(as.formula(modeltext()),
            data = data,
            outline = input$outliers)
  })
  
  output$fit <- renderPrint({
    summary(fit)
  })
  
  output$OzonePlot <- renderPlot({
    with(data, {
      plot(as.formula(modeltext()))
           abline(fit(), col = 2)
           })
    })
  
})
```


## Usage

1. Selcet the variable you want
2. Observe the plot



